Cluster Paper

### 2015-04-24 ms.tex
add cluster CMD

\subsection{Full Knowledge}
We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$. \editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight. I don't think that will be the case when we get more complicated things.}

@@

\begin{figure} 
	\includegraphics[width=0.49\textwidth]{oii_sdss.pdf} 
	\caption{} \label{fig:oii sdss} 
\end{figure}

@@

>>>>

\subsection{Full Knowledge}
We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos \editorial{these are old numbers, the current is something like 650,000 galaxies, and 16,000 halos}, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$. \editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight. I don't think that will be the case when we get more complicated things.}

@@

\begin{figure} 
	\includegraphics[width=0.49\textwidth]{oii_sdss.pdf} 
	\caption{177107 galaxies} \label{fig:oii sdss} 
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.49\textwidth]{clustersCMD.pdf}
	\caption{657916 galaxies}
	\label{fig:oii clusters}
\end{figure}
